Compare findings

### 2017-06-05 Code/validation/4 SH_examine_comparisons.Rmd

---
title: "Compare findings"
output: github_document
---

@@

```{r read_data}
le.table <- read.csv("~/BlackWhiteMortalityGap/Code/3_validation/le_table.csv", header = T)
SH.dat <- read.csv("~/SH_HA_supp_app_data.csv", header = T)
```

@@

write.csv(compare.le, "~/BlackWhiteMortalityGap/Code/3_validation/compare_LE.csv")
```

>>>>

---
title: "Compare findings"
output: html_document
---

In this file we compare the LE estimates for Sam's Health Affairs paper to estimates we get from running our model on his data. 
Thus the goal of this exercise is to answer the questions "are the models doing the same thing?"

@@

```{r read_data}
le.table <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Code/validation/le_table.csv", header = T) 
#le_table was created in the SH_comparison.R file

SH.dat <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Data/SH_HA_supp_app_data.csv",
                   header = T) #supplementary appendix data -- so Sam's original estimates
```

@@

write.csv(compare.le, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Code/validation/compare_LE.csv")
```
